Percussive Sound Generation with Virtual Listeners and Modular Synthesizers

### 2020-01-31 paper.tex
Updates from Overleaf

\todo[inline, color=green!30]{I think it might be worthwhile to point out the potential in our work for live performance, compared to other works which use 3rd party VSTs, require pre-training and user interaction, would that be appropriate for a scientific paper? should it be done here or in related work?}
\subsection{Methodology}
Towards our goal of generating original audio, we found the proper implementation of 2 major components to be crucial:
\begin{itemize}
    \item \textit{Virtual Synthesizer}:A flexible, deterministic, and tractable generator which can create audio. The core of our implementation made use of pippi, \footnote{https://github.com/luvsound/pippi} a fast, offline focused python DSP library with a C backend. We additionally used the scipy \cite{jones2001scipy} library a few audio effects that we found lacking in pippi. 
    \item \textit{Virtual Ear}: An ear that returns an evaluation of an audio sample; estimating the effectiveness of an audio sample's fulfillment of a producers requirements. The ear's evalutations guides the generation process towards a desired path, making the implementation and training of the ear crucial to the sounds which are generated. A particularly effective implementation was done by using a labeled set of percussive and non-percussive audio files to train a custom model (combination of a simple Convolutional Neural Net (CNN) and a custom envelope estimation algorithm), giving us a "virtual drum detector ear". \\
\end{itemize}
Our components are designed with modularity and parallelizability in mind. This allows each component to be debugged, modified and improved without requiring modifications in other components; additionally increasing the scalability and speed of experiments.
Section \ref{impl} contains further discussion of the components as well as the code that glues the project together.\\ 
While the main focus of this project is the generation of novel percussive sounds, our methodology indicates promising results with regards to creation of new presets for any virtual synth without the need for a-priori knowledge of the functions of its parameters (i.e the effect of parameter modulation on the sonic output). We also demonstrate the viability of a few lesser explored avenues for the purposes of audio synthesis and Music Information Retrieval (MIR), notably:
\begin{enumerate}[label=\roman*]
\item Heuristic search methods for the creation of new presets for virtual synthesizers. More concretely, we observed that given a virtual ear which could reliably score pieces of audio based on its resemblance to a desired category (e.g:kicks,snares,piano), we were able to rapidly search the parameters of a virtual synthesizer and create numerous parameter-sets (i.e presets) which resemble our desired category of sounds.
\item The viability of virtual synthesizers based on Digital Signal Processing (DSP) methods for fast, unsupervised creation of novel audio, discussed in more detail in section \ref{related}. \\
\end{enumerate}

@@

\subsection{Data And Project Replication}
\label{data}
\colorbox{green!=30}{One last thing to do, will take a 1 day}\\
\colorbox{green!=30}{need to finalize database}\\
\colorbox{blue!=30}{Should this section be at the start of the paper?The End? Appendix?}\\
talk about  categories, sources, data processing. 
Code for the data processing is written, I need to download the no-copyright sounds, run the code and host the results. 
Give link for people to download it, show where to find the scripts for database expansion.
\section{Implementation}
\label{impl}
\subsection{Virtual Synthesizer}
We used the python based Pippi library for sound generation\footnote{https://github.com/luvsound/pippi}. This library uses a C back-end and focuses on fast offline generation of audio signals. In our implementation, a synthesizer can have any number of submodules. The parameters that deterministically dictate the output signal of the submodule as well as the range of values each paramter can take are shown in table 1 \ref{table:1} We call this number the \textit{stack size}. For the range of parameters each submodule can take. We call the sets of parameters that characterize a Synth's submodules a \textit{program} (analogous to a preset).  Each submodule can make an audio signal with the length of 0.1-1 second. If a Synth has a stack size of more than 1, these audio signals are overlapped and the total amplitude is normalized.\\
\begin{table}[h!]
\centering
\resizebox{\columnwidth}{!}{\begin{tabular}{ |c|c|c| } 
\hline
Parameters & Value Range & notes and constraints\\
\hline \hline
Attack & 0-3 & A-D-S-R values relative\\
Decay & 0-3 & relative to A-S-R\\
Sustain & 0-3 & relative to A-D-R\\
Release & 0-3 & relative to A-D-S\\
OSC type & sine,square,saw & tone type\\
IsNoise & boolean & whether to generate noise\\
Sample Length & 0-1 second & - \\
StartTime & 0-1 second & Length+Start<1\\
Amplitude & 0.1-1 & 1 = max amplitude\\
Pitches(notes) & list of pitches &  range of C0(16.35hz) to B9 \\
HP filter Cuttoff & 0-20000 & -\\
LP filter Cuttoff & 20000-HP & never lower than HP cutoff\\
Filter Order & 4,8,16 & butterworth filter order \\
\hline
\end{tabular}}
\caption{Synthesizer Submodule Parameters. Despite the simplicity of the paramters and our efforts at constraining the ranges, the number of paramters that can be randomly chosen for each submodule is in the order of $10^{15}$ }
\label{table:1}
\end{table}
\begin{figure*}[h]
\centering

@@

@@

  In our case, as discussed in section \ref{survey}, the majority of sounds generated by the synth do not resemble percussion. Even if we only consider 1 second long sounds made with a single stacked synth, the set of synthesizer parameters (and we assume, the sound generated by these paramters) is extremely large. In our case, we determined that there are 2 steps necessary to effectively extract percussive sounds from the randomly generated noise from the virtual synthesizer: 

@@

   \item  $Task\,1$: Binary separation of sounds with percussive features from non-percussive sounds.
   \item $Task\,2$: Given confidence that of the sound being categorized is percussive, categorizing the type of drum.

@@

We are interested in extracting generalize features that can be applied in other audio domains. In this work we rely entirely on Fast Fourier Transform (FFT) and by extension Short-time Fourier Transforms (STFT) for feature extraction. Using FFT, a signal can be represented by a vector with each index corresponding to a frequency-bin (a range of frequencies too close to be distinguishable) and the value of the index corresponding to the combined-magnitude of the frequencies within the bin. STFT can be employed when a more accurate representation is desired via the application of the FFT to a sliding time-window on the signal to create a matrix (a list of vectors). This matrix can effectively represent the frequencies present in the signal at each time step, given the right window-length and hop-size (how much the window is shifted at each time-step).\\

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.8\linewidth]{images/cnn_ear.png}
\caption{confusion matrix of the model working well on a test set. \colorbox{green!=30}{will be updated with new ear.}}
\label{fig:ok ear}
\end{figure}
\todo[inline,color=green!30]{ will add f-measure calculations and other confidence inducing graphs (for example I have a grid of spectrums with the ear's guess vs the actual label under each spectrum, I can colorize the grid depending on whether the guess was correct or not). Code in the notebooks. After updating ear, I will make them look presentable and add them.}
%
% How Can The Synth and Ear Interact?
%
\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{images/random_ranks.png}
\caption{\colorbox{green!=40}{labels bigger + show other stack sizes} Showing proportions of categorical ranks for around 50,000 randomly generated sounds. Only showing ranks 1-5. About 90\% received the rank of 1 (blue portion of the bar) for the "synth" category, meaning that the ear correctly gave the highest probability to the sound being from a synth combination. We are interested in the small percentages of random generations that trick the ear due to coincidentally being similar to actual drums (i.e those who received a rank of 1) }
\label{fig:rank portions}
\end{figure}

@@

\section{Novel Generations}
\label{gens}
\subsection{The Goal}
 Given a category, our aim is to use random generations to guide an algorithm towards novel generation of drums for that category. We evaluate each method by measuring how many samples of categories \textit{kick,snare} and \textit{hat} can be produced in under a minute. Finally we show results of a survey conducted to measure the quality of these samples. 
\subsection{General Methods}
\colorbox{green!=30}{The next 3 sections will be modified heavily after the ear is updated.}
\subsubsection{Random Generation}
To establish a benchmark, we seek to establish the likelihood of generating samples of each category if we generate programs for various stack sizes by random selection of parameters. We have observed a bias in generations as indicated in figure \ref{gens}.\\
\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
\includegraphics[width=0.48\linewidth]{example-image-a}
\includegraphics[width=0.48\linewidth]{example-image-a}
\label{fig:1stack}
\setcounter{subfigure}{2}%
\end{subfigure}
\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosesn categories in under a minute}
\label{fig:rand-graphs}
\end{figure}
% \subsubsection{Multivariate Distribution Sampling}
% This method is extremely fast and scalable once the parameter space is calculated. But success is limited due to well known issues with this approach. Notably that the parameter space for virtual synthesizers are often neither differentiable nor Gaussian. \cite{esling2019universal} (a couple more papers also talked about this, \colorbox{green!=40}{I have to look them up}). Currently our parameters are array indices mapping to different values for Synth components. This makes the assumption that our discrete parameter space is normally distributed or differentiable in-appropriate and prone to errors. \\
\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
\includegraphics[width=0.48\linewidth]{example-image-b}
\includegraphics[width=0.48\linewidth]{example-image-b}
\label{fig:1stack}
\setcounter{subfigure}{2}%
\end{subfigure}
\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosen categories in under a minute}
\label{fig:multi-graphs}
\end{figure}

\subsubsection{Evolutionary Search}
We implemented evolutionary search using DEAP \citep{DEAP_JMLR2012}. A parameter set is assumed to be an individual with each parameter being its genes. To measure an individuals fitness, we use the formula $fitness=score-rank$. As generations evolve, a Hall-of-Fame list with a fixed size tracks the best individuals to ever live in any given generation, updating itself after each batch of off-springs is evaluated.\\
To ensure diversity of the HOF individuals, the fitness score should also consider some measure of uniqueness. A weighted minkowski distance \footnote{https://docs.scipy.org/doc/scipy/reference/generated/scipy.spatial.distance.minkowski.html} between the genes of an offspring and the HOF individuals may be a good measurement.\\
A generation of $N$ individuals are initialized randomly. To create the offspring generation, each generation goes through mutations and in-place gene crossovers. The new generation consists of the top 80\% of the offspring generation and 20\% new individuals to quicken gene diversity. If the new individuals are coming directly from previously measured high scoring parameter sets, we ensure that they cannot be directly added to HOF without going through mutations and crossovers first.\\
\subsubsection{Survey of Generated Drums}
\label{survey}
To measure the quality of the samples produced by our pipeline, we randomly generated around 50-60 samples in the following categories: "snare","kick","hat","clap" and "other" (combination of rims,shakers, and unusal percussive sounds"). These samples were determined to be percussive and then categorized by 4 different models (FC,CNNLSTM,E+F and AVG). We ensured a balanced division between samples of stack sizes 1,2 and 4 (each stack is responsible for a third samples under each category). Both writers then categorized these samples without knowledge of other categorizations (human or computation models). It's important to note that:
\begin{itemize}
    \item Humans had an additional category of "bad" for samples that they deemed not appropriate. 
    \item Human's had the same categorization in 47\% of cases
    \item The agreement between the authors and AVG was 44\% and 47\%, not significantly lower than agreement with each other. 
    \item Of 257 samples, both authors agreed with FC, CNNLSTM, AVG and E+F respectively in 78,76,76 and 46 of cases.
\end{itemize}
We assess the reliability of agreement between humans and categorization models via the Fleiss' kappa coefficient. The value of 0 or less for this coefficient indicates no agreement beyond random chance, and the value of 1 indicating perfect agreement. Our kappa measurements \ref{kappa_table} lie in within the 3.5-4.5 range, indicating mild to moderate agreement between humans and machines. We again measure this coefficient after dropping samples that were categorized as "bad" by the authors, as samples that humans deem to be "bad" indicate a failure in phase 1 and arguably should not have been categorized by the models at all. Dropping of samples that both authors deemed "bad" causes 8\% reduction of our data (21 samples) and a small increase in kappa score. Dropping samples either reviewer deemed bad resulted in a 30\% reduction of samples and relatively large increase in kappa scores. \\
\begin{center}
\begin{table}

 \begin{tabular}{||c c c c c c||} 
 \hline
 DropBad? & Sample Size & HvH & H+FC & H+CNN & H+ALL \\ [0.5ex] 
 \hline
 No & 257 &0.37 & 0.35 & 0.35 & 0.36 \\ 
 \hline
 Yes(if both)& 236 & 0.31 & 0.37 & 0.37 & 0.38 \\
 \hline
 Yes(if either)& 180 & 0.47 & 0.50 & 0.48 & 0.46 \\
 \hline

\end{tabular}
\caption{\label{kappa_table}Table of Fleiss' kappa coefficient to measure the degree of agreement between humans (HvH), humans and FC model (H+FC), humans and CNNLSTM model and humans and all models (H+ALL)}
\end{table}

\end{center}

@@

\begin{itemize}
    \item Our methodology was successful in generating novel examples of some percussion categories.
    \item Reiterate the importance of ear.
    \item There are potential benefits (e.g: pedagogical, software engineering, efficiency, data search, generality of solution, etc.) to separate some audio generation tasks into multiple parts, rather than throwing everything at some neural net. 
    \item With the right implementation of DSP methods to create a synth, Genetic search (viewed as too slow by previous work) is viable for finding  desired programs and parameters.
    \item Neural nets are function approximators. You don't need them if the actual function is understandable and simple...(but is our task simple enough? how do I prove it?)
    \item When possible, using DSP methods instead of NNs is preferable in many ways(speed,computation,hardware requirements).\\
    \colorbox{green!=30}{Include some speed measurements in appendix?}
    \item ...
\end{itemize}
\section{Future Work}
\colorbox{blue!=30}{Need to think about this more}
\begin{itemize}
    \item Potential for other generative methods (e.g reinforcement learning)
    \item Making the synth's sound range more diverse while maintaining speed and efficiency
    \item Can our approach be used for VSTs?
\end{itemize}

\section{Ethical Standards}
We affirm that our work follows the principles of ethical and professional conduct.
\bibliographystyle{abbrv}
    \bibliography{nime-references} 
\end{document}

>>>>

\subsection{Methodology}
Towards our goal of generating original audio, we found the proper implementation of 2 major components to be crucial:
\begin{itemize}
    \item \textit{Virtual Synthesizer}:A flexible, deterministic, and tractable generator which can create audio. The core of our implementation made use of pippi, \footnote{https://github.com/luvsound/pippi} a fast, offline focused python DSP library with a C backend. We additionally used the scipy \cite{jones2001scipy} library a few audio effects that we found lacking in pippi. 
    \item \textit{Virtual Ear}: An ear that returns an evaluation of an audio sample; estimating the effectiveness of an audio sample's fulfillment of a producers requirements. The ear's evalutations guides the generation process towards a desired path, making the implementation and training of the ear crucial to the sounds which are generated. A particularly effective implementation was done by using a labeled set of percussive and non-percussive audio files to train a custom model (combination of a simple Convolutional Neural Net (CNN) and a custom envelope estimation algorithm), giving us a "virtual drum detector ear". \\
\end{itemize}
Our components are designed with modularity and parallelizability in mind. This allows each component to be debugged, modified and improved without requiring modifications in other components; additionally increasing the scalability and speed of experiments.
Section \ref{impl} contains further discussion of the components as well as the code that glues the project together.\\ 
While the main focus of this project is the generation of novel percussive sounds, our methodology indicates promising results with regards to creation of new presets for any virtual synth without the need for a-priori knowledge of the functions of its parameters (i.e the effect of parameter modulation on the sonic output). We also demonstrate the viability of a few lesser explored avenues for the purposes of audio synthesis and Music Information Retrieval (MIR), notably:
\begin{enumerate}[label=\roman*]
\item Heuristic search methods for the creation of new presets for virtual synthesizers. More concretely, we observed that given a virtual ear which could reliably score pieces of audio based on its resemblance to a desired category (e.g:kicks,snares,piano), we were able to rapidly search the parameters of a virtual synthesizer and create numerous parameter-sets (i.e presets) which resemble our desired category of sounds.
\item The viability of virtual synthesizers based on Digital Signal Processing (DSP) methods for fast, unsupervised creation of novel audio, discussed in more detail in section \ref{related}. \\
\end{enumerate}

@@

\subsection{Data And Project Replication}
\label{data}

talk about  categories, sources, data processing. 
Code for the data processing is written, I need to download the no-copyright sounds, run the code and host the results. 
Give link for people to download it, show where to find the scripts for database expansion.
\section{Implementation}
\label{impl}
\subsection{Virtual Synthesizer}
We used the python based Pippi library for sound generation\footnote{https://github.com/luvsound/pippi}. This library uses a C back-end and focuses on fast offline generation of audio signals. In our implementation, a synthesizer can have any number of submodules. The parameters that deterministically dictate the output signal of the submodule as well as the range of values each paramter can take are shown in table 1 \ref{table:1} We call this number the \textit{stack size}. For the range of parameters each submodule can take. We call the sets of parameters that characterize a Synth's submodules a \textit{program} (analogous to a preset).  Each submodule can make an audio signal with the length of 0.1-1 second. If a Synth has a stack size of more than 1, these audio signals are overlapped and the total amplitude is normalized.\\
\begin{table}[h!]
\centering
\resizebox{\columnwidth}{!}{\begin{tabular}{ |c|c|c| } 
\hline
Parameters & Value Range & notes and constraints\\
\hline \hline
Attack & 0-3 & A-D-S-R values relative\\
Decay & 0-3 & relative to A-S-R\\
Sustain & 0-3 & relative to A-D-R\\
Release & 0-3 & relative to A-D-S\\
OSC type & sine,square,saw & tone type\\
IsNoise & boolean & whether to generate noise\\
Sample Length & 0-1 second & - \\
StartTime & 0-1 second & Length+Start<1\\
Amplitude & 0.1-1 & 1 = max amplitude\\
Pitches(notes) & list of pitches &  range of C0(16.35hz) to B9 \\
HP filter Cuttoff & 0-20000 & -\\
LP filter Cuttoff & 20000-HP & never lower than HP cutoff\\
Filter Order & 4,8,16 & butterworth filter order \\
\hline
\end{tabular}}
\caption{Synthesizer Submodule Parameters. Despite the simplicity of the paramters and our efforts at constraining the ranges, the number of paramters that can be randomly chosen for each submodule is in the order of $10^{15}$ }
\label{table:1}
\end{table}
\begin{figure*}[h]
\centering

@@

\subsubsection{Feature Extraction}

@@

  In our case, as discussed in section \ref{survey}, the majority of sounds generated by the synth do not resemble percussion. Even if we only consider 1 second long sounds made with a single stacked synth, the set of synthesizer parameters (and we assume, the sound generated by these parameters) is extremely large. In our case, we determined that there are 2 steps necessary to effectively extract percussive sounds from the randomly generated noise from the virtual synthesizer: 

@@

   \item  $Phase1\,1$: Binary separation of sounds with percussive features from non-percussive sounds.
   \item $Phae2\,2$: Given confidence that the sound being categorized is percussive, categorizing the type of drum or percussion.

@@

We are interested in extracting generalize features that can be applied in other audio domains. In this work we rely entirely on Fast Fourier Transform (FFT) and by extension Short-time Fourier Transforms (STFT) for feature extraction. Using FFT, a signal can be represented by a vector with each index corresponding to a frequency-bin (a range of frequencies too close to be distinguishable) and the value at each index corresponding to the combined-magnitude of the frequencies within the bin. STFT can be employed when a more accurate representation is desired; via the application of the FFT to a sliding time-window on the signal to create a matrix (a list of vectors). This matrix can effectively represent the frequencies present in the signal at each time step, given the right window-length and hop-size (how much the window is shifted at each time-step).\\

@@

\subsubsection{The Models}
Using the described features, we trained several models for Phase 1 and 2. These include Fully-Connected (FC) models, Convolutional Neural Nets (CNNs) and CNN+Long Term Short Memory models (CNNLSTM). The task of phase 1 is to separate drums from not-drums (DrumVsNotDrum, or DVN). The task of phase to is to categorize drums and percussion (DrumVsDrum, or DVD). We kept our feature space small, making it viable to for the task of designing models and picking the right features being done on a trial and error basis. A summary of models utilized in our pipeline is given below:
\begin {enumerate}
\item FC-DVN: A small fully connected network trained on Envelope features, reaching 97\% accuracy on our test data for phase 1. 
\item CNNLSTM-DVN: A combination of CNN and LSTM models, where the CNN model extracts higher level features that are fed temporally to an LSTM cell. This model is trained on spectrum data and reaches 98\% on our test set for phase 1.
\item E+F-DVD: A fully connected model trained on a concatenation of envelope and frequency features for phase 2. Reaching 80\% accuracy for 6-way drum categorization.
\item CNN-DVD: A deep CNN model that reaches used for phase 2. 82\% accuracy in a 6-way drum categorization. Trained on Spectrum features.
\item FC-DVD: Fully connected 3 layer neural net with 78\% accuracy for 6-way drum categorization. Trained on Spectrum features.
The number of parameters for these models were picked rather arbitrarily. We'd like to note that based on our anecdotal observations, the minor modifications in features played a much more significant role in the model accuracy than major parameter changes. Also as discussed in section \ref{survey}, despite it's marginally lower accuracy rate, the FC-DVD model has a slight but noticeable advantage in regards to matching human categorization of data. Likewise, Freq+Env had a much lower degree of agree-ability with humans, despite its better performance on organic drum data. Leading us to believe that model accuracy on test data alone cannot be relied upon when the domain of sounds being categorized is switched from organic samples to a virtual synth. \\
With our models showing efficacy at categorizing organic drums vs randomly generated synth sounds, and categorizing organic drums accurately, we combine models in order to increase the efficacy of each phase and address the "open set" problem for our task. For phase 1, we only determine sounds as percussive if both FC-DVN and CNN-LSTM have determined it as such with over 90\% confidence. For the majority of our random generations, that is not the case, but if a randomly generated sound is passed this phase, our three categorizers assign their categorizations to this sound. These categorizers have a moderate degree of agree-ablity, as seen in \ref{survey}, but often there is not a unanimous decision. The Fourth method of categorization, "averaged-cat", is implemented by taking the sum of the softmax outputs of all three categorizers and use this sum to determine the category. \\
These models can be combined and weighted in various ways, the confidence thresholds can be modified in order to implement "ears" with different properties. A glaring issue in the current implementation is the treatment of softmax outputs as a reasonable measure of a models confidence. For various reasons, some models tend to have much higher confidence in their scores, skewing attempts at finding a consensus.

% How Can The Synth and Ear Interact?
%
\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{images/random_ranks.png}
\caption{\colorbox{green!=40}{labels bigger + show other stack sizes} Showing proportions of categorical ranks for around 50,000 randomly generated sounds. Only showing ranks 1-5. About 90\% received the rank of 1 (blue portion of the bar) for the "synth" category, meaning that the ear correctly gave the highest probability to the sound being from a synth combination. We are interested in the small percentages of random generations that trick the ear due to coincidentally being similar to actual drums (i.e those who received a rank of 1) }
\label{fig:rank portions}
\end{figure}

@@

\section{Novel Generations}
\label{gens}
\subsection{The Goal}
 Given a category, our aim is to use random generations to guide an algorithm towards novel generation of drums for that category. We evaluate each method by measuring how many samples of categories \textit{kick,snare} and \textit{hat} can be produced in under a minute. Finally we show results of a survey conducted to measure the quality of these samples. 
\subsection{General Methods}
\subsubsection{Random Generation}
To establish a benchmark, we seek to assess the likelihood of generating samples of each category if we generate programs for various stack sizes by random selection of parameters. We have observed a bias in generations as indicated in figure \ref{gens}.\\

% \subsubsection{Multivariate Distribution Sampling}
% This method is extremely fast and scalable once the parameter space is calculated. But success is limited due to well known issues with this approach. Notably that the parameter space for virtual synthesizers are often neither differentiable nor Gaussian. \cite{esling2019universal} (a couple more papers also talked about this, \colorbox{green!=40}{I have to look them up}). Currently our parameters are array indices mapping to different values for Synth components. This makes the assumption that our discrete parameter space is normally distributed or differentiable in-appropriate and prone to errors. \\

\subsubsection{Evolutionary Search}
We implemented evolutionary search using DEAP \citep{DEAP_JMLR2012}. A parameter set is assumed to be an individual with each parameter being its genes. To measure an individuals fitness, we use the formula $fitness=score-rank$. As generations evolve, a Hall-of-Fame list with a fixed size tracks the best individuals to ever live in any given generation, updating itself after each batch of off-springs is evaluated.\\
To ensure diversity of the HOF individuals, the fitness score should also consider some measure of uniqueness. A weighted minkowski distance \footnote{https://docs.scipy.org/doc/scipy/reference/generated/scipy.spatial.distance.minkowski.html} between the genes of an offspring and the HOF individuals may be a good measurement.\\
A generation of $N$ individuals are initialized randomly. To create the offspring generation, each generation goes through mutations and in-place gene crossovers. The new generation consists of the top 80\% of the offspring generation and 20\% new individuals to quicken gene diversity. If the new individuals are coming directly from previously measured high scoring parameter sets, we ensure that they cannot be directly added to HOF without going through mutations and crossovers first.\\
\subsubsection{Survey of Generated Drums}
\label{survey}
To measure the quality of the samples produced by our pipeline and the power of our models, we randomly generated around 50-60 samples in the following categories: "snare","kick","hat","clap" and "other" (combination of rims, 
shakers and unusal percussive sounds"). These samples were determined to be percussive and then categorized by 4 different models (FC,CNNLSTM,E+F and AVG). We ensured a balanced division between samples of stack sizes 1,2 and 4 (each stack is responsible for a third samples under each category). Both writers then categorized these samples without knowledge of other categorizations (human or computation models). It's important to note that:
\begin{itemize}
    \item Humans had an additional category of "bad" for samples that they deemed not percussive. The "bad" category indicates that the sample should have been skipped in phase 1. 
    \item With 6 categorization groups, human's had the same categorization in 47\% of cases
    \item The agreement between the humans and AVG was 44\% and 47\%, not significantly lower than agreement with each other. 
    \item Of 257 samples, both humans agreed with FC, CNNLSTM, AVG and E+F respectively in 78, 76, 76 and 46 of cases.
\end{itemize}
We assess the reliability of agreement between humans and categorization models via the Fleiss' kappa coefficient \cite{fleiss1971measuring}. The value of 0 or less for this coefficient indicates no agreement beyond random chance, and the value of 1 indicating perfect agreement. Our kappa measurements \ref{kappa_table} lie within the 3.5-4.5 range, indicating mild to moderate agreement between humans and machines. We again measure this coefficient after dropping samples that were categorized as "bad" by the authors, as samples that humans deem to be "bad" indicate a failure in phase 1 and arguably should not have been categorized by the models at all. Dropping of samples that both authors deemed "bad" causes 8\% reduction of our data (21 samples) and a small increase in kappa score. Dropping samples either reviewer deemed bad resulted in a 30\% reduction of samples and relatively large increase in kappa scores. \\

Possible takeaways from this survey:
\begin{itemize}
    \item The survey brings into question the reliability of our phase 1 models, as 30\% of the generated samples were deemed not percussive by at least 1 reviewer and 8\% by both reviewers
    \item The task of categorizing synthetic drums is difficult. Survey shows that the scale of agreement within humans as well as between humans and various model combinations is moderate at best, even after removal of "bad" samples.  While the same models can easily achieve 98+ percent accuracy when tested on organic drum samples. This may be a manifestation of the "open set recognition" problem. 
    \item While there is much room for improvement, our pipeline can generate and categorize drums and percussive sounds with a promising degree of success. 
\end{itemize}
\begin{center}

\begin{table}
 \resizebox{\linewidth}{!}{\begin{tabular}{||c c c c c c c||} 
 \hline
 Drop Bad? & Size & HvH & H+FC & H+CNN & H+ALL & 3 models \\ [0.5ex] 
 \hline
 No & 257 &0.37 & 0.35 & 0.35 & 0.36 & 33\\ 
 \hline
 if both & 236 & 0.31 & 0.37 & 0.37 & 0.38 & 33 \\
 \hline
 if either& 180 & 0.47 & 0.50 & 0.48 & 0.46 &  0.37 \\
 \hline
\end{tabular}}
\caption{\label{kappa_table}Table of Fleiss' kappa coefficient to measure the degree of agreement between humans (HvH), humans with FC model (H+FC), humans with CNNLSTM model, humans with all models (H+ALL), and the 3 models }
\end{table}
\end{center}

@@

\begin{itemize}
    \item Our methodology was successful in generating novel examples of some percussion categories.
    \item Reiterate the importance of ear.
    \item There are potential benefits (e.g: pedagogical, software engineering, efficiency, data search, generality of solution, etc.) to separate some audio generation tasks into multiple parts, rather than throwing everything at some neural net. 
    \item With the right implementation of DSP methods to create a synth, Genetic search (viewed as too slow by previous work) is viable for finding  desired programs and parameters.
    \item Neural nets are function approximators. You don't need them if the actual function is understandable and simple...(but is our task simple enough? how do I prove it?)
    \item When possible, using DSP methods instead of NNs is preferable in many ways(speed,computation,hardware requirements).\\
    \colorbox{green!=30}{Include some speed measurements in appendix?}
    \item ...
\end{itemize}
\section{Future Work}
\begin{itemize}
    \item Potential for other generative methods (e.g reinforcement learning)
    \item Making the synth's sound range more diverse while maintaining speed and efficiency
    \item Can our approach be used for VSTs?
\end{itemize}

\section{Ethical Standards}
We affirm that our work follows the principles of ethical and professional conduct. No drums were harmed in the making of this paper.
\bibliographystyle{abbrv}
    \bibliography{nime-references} 
\end{document}
